%!TEX TS-program = pdflatex
\documentclass{mycv}

\hypersetup{%
  pdftitle={Christos Dalamagkas - Curriculum Vitae},
  pdfauthor={Christos Dalamagkas},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Christos Dalamagkas}
}

\begin{document}
	\thispagestyle{plain}

	\name{Christos Dalamagkas}{Contract Researcher}{Network Engineer (CCNA)}
	\contact{(+30) 698 316 0295}{me@cdalamagkas.gr}{chris.dal}{https://cdalamagkas.gr}{linkedin.com/in/cdalamagkas}{cdalamagkas}{0000-0002-0210-5290}
	\textbf{Location}: Athens, Greece

	%
	%\vspace*{-0.75cm}
	%
    \section{Education}
	\begin{EntryDatedLogo}{Democritus University of Thrace}{https://cs.duth.gr/}{2023 - Now}{PhD Candidate, Dept. of Computer Science}{-0.6cm}{duth}{0.6}
		\begin{Itemize}
			\item Software-Defined Network Techniques for Orchestrating and Protecting Industrial Internet of Things
		\end{Itemize}
	\end{EntryDatedLogo}

	\vspace*{0.5cm}
	
	\begin{EntryDatedLogo}{University of Western Macedonia}{http://ece.uowm.gr}{2012 -- 2017}{M.Eng. (5 years of study), Dept. of Informatics and Telecommunications Engineering}{-1.25cm}{uowm}{0.6}
		\begin{Itemize}
			%\item Recognized as integrated master degree (level 7 of EFQ) under government gazette 3987/14-9-2018
			%\item Thesis title: "\textit{Design of Market Mechanism for Dynamic Bandwidth Allocation on XG-PON}".
			\item Game Theory on XG-PON networks: \url{https://dspace.uowm.gr/xmlui/handle/123456789/835}.
			\item Graduation Grade: 8.2/10.
		\end{Itemize}
	\end{EntryDatedLogo}
	
	\section{Experience}
	\begin{EntryDatedLogo}{Metamind Innovations P.C. (MINDS)}{https://metamind.gr/}{May 2018 - Now}{Associate Researcher}{-1.25cm}{minds}{0.6}
		\begin{Itemize}
			\item Researcher for EU-funded programmes: \href{https://cordis.europa.eu/project/id/101122357}{D-HYDROFLEX HE}.
			\item Product Manager \& Developer: MINDS SDN Controller \& Dashboard, MINDS RADAR.
			\item Research topics: Industrial IoT, Cybersecurity.
		\end{Itemize}
	\end{EntryDatedLogo}

	\vspace*{0.5cm}
	
	\begin{EntryDatedLogo}{Public Power Corporation S.A. (PPC)}{https://www.dei.gr/en}{May 2018 - Now}{Contract Researcher}{-3cm}{dei}{0.6}
		\begin{Itemize}
			\item Project Manager and Researcher for EU-funded programmes: \href{https://cordis.europa.eu/project/id/101070450}{AI4CYBER HE}, \href{https://cordis.europa.eu/project/id/101070455}{DYNABIC HE}, \href{https://cordis.europa.eu/project/id/101070586}{PHOENI2X HE}, \href{https://cordis.europa.eu/project/id/101056765}{EV4EU HE}.
			\item Succesfully completed EU-funded projects: \href{https://cordis.europa.eu/project/id/787011}{SPEAR H2020}, \href{https://cordis.europa.eu/project/id/833955}{SDN-microSENSE H2020}, \href{https://cordis.europa.eu/project/id/957406}{TERMINET H2020}, \href{https://www.jaunty.eu/}{JAUNTY Erasmus+}, \href{https://cordis.europa.eu/project/id/101021936}{ELECTRON H2020}.
			\item Product Manager \& Developer: \href{https://github.com/EV4EU/ov2xmp}{Open V2X Management Platform} 
			\item Research topics: Industrial IoT, Software-Defined Networking, Cybersecurity.
			\item System Administrator for the Industrial Internet of Things Laboratory of \href{https://innovationhub.dei.gr/el/}{PPC Innovation Hub}.
		\end{Itemize}
	\end{EntryDatedLogo}
	
	\vspace*{0.5cm}
	
	\begin{EntryDatedLogo}{Freelance ICT Engineer}{https://cdalamagkas.gr}{Jun. 2018 - 2023}{Field Engineer}{-1cm}{engineer}{0.6}
		\begin{Itemize}
			\item Freelancer CCNA Network Engineer.
			\item Field Engineer for IT outsourcing companies.
		\end{Itemize}
	\end{EntryDatedLogo}

	\vspace*{0.5cm}	

	%\begin{EntryDatedLogo}{University of Western Macedonia}{https://ece.uowm.gr}{Mar. 2017 - Now}{Research Assistant}{-1cm}{uowm}{0.6}
	%	\begin{Itemize}
	%		\item Teaching assistance for Computer Networks, Cybersecurity and Event-driven simulation.
	%		\item Assistance in EU-funded research programmes.
	%		\item Developer (Web development, SDN), DevOps. 
	%	\end{Itemize}
	%\end{EntryDatedLogo}

	%\vspace*{0.5cm}

	\begin{EntryDatedLogo}{IEK ALFA (Vocational school)}{https://iekalfa.gr}{Oct. 2018 - Jun. 2019}{Teacher}{-1cm}{alfa}{0.6}
		\begin{Itemize}
			\item Computer Networks, Telecommunications, Operating Systems, Object-oriented Programming (C++).
			\item Course Material: \url{https://github.com/cdalamagkas/cs-lectures-gr}
		\end{Itemize}
	\end{EntryDatedLogo}
		
	%\begin{EntryDatedLogo}{University of Brighton}{https://www.brighton.ac.uk}{Jul. - Sept. 2017}{Research assistant}{-0.45cm}{brighton}{0.6}
	%	\begin{Itemize}
	%		\item Research on XG-PON and NG-PON2 networks.
	%		\item Development of NG-PON2 simulator in MATLAB.
	%		\item Worked on a novel MAC algorithm for NG-PON2.	
%	\end{Itemize}
	%\end{EntryDatedLogo}

	%\vspace*{0.5cm}	

	%\begin{EntryDatedLogo}{IntelliSolutions S.A}{http://intelli-corp.com}{Jul. - Aug. 2016}{Systems and Network Engineer (Intern)}{-0.4cm}{intelli}{0.75}
	%\begin{Itemize}
	%	\item Design and implementation of new enterprise network.
	%	\item Network security planning and implementation (pfSense, OpenVPN, firewall, squid).
	%	\item Windows Server, Active Directory and SQL failover cluster setup, type 2 virtualization (VMware).
	%\end{Itemize}
	%\end{EntryDatedLogo}
		
	\section{Professional Certifications}
	\begin{EntryDatedLogo}{Cisco Certified Network Associate (CCNA)}{https://www.cisco.com/}{\scshape{Jul. 2019}}{}{-0.75cm}{cisco}{0.6}
	\end{EntryDatedLogo}
	
	\section{Skills}
	\begin{tabular}{m{4.5cm} m{13cm}}\renewcommand{\arraystretch}{2}
		\textbf{Computer Networking}   	& \textbf{Cisco IOS}, \textbf{Open vSwitch}, \textbf{ArubaOS-Switch}, \textbf{OpenFlow}, \textbf{Python Ryu}.\\
		\textbf{Cybersecurity}			& \textbf{pfSense}, \textbf{OpenVPN}, \textbf{Python Scapy}, \textbf{Wazuh}, \textbf{Shuffle.io}, OIDC, PKI.\\
		\textbf{Virtualization}			& \textbf{Proxmox VE}, XCP-ng, VMware Workstation, VirtualBox.\\ 
		\textbf{DevOps}					& \textbf{Docker}, \textbf{GitLab CI/CD}. \\
		\textbf{Programming} 	    	& \textbf{Python}, \textbf{JavaScript}, \textbf{Django}, \textbf{MATLAB}, Java, C/C++. \\
		\textbf{Industrial IoT}			& \textbf{Modbus TCP}, \textbf{MQTT}, \textbf{OCPP 1.6-J}.\\
		\textbf{Telecommunications}   	& ITU-T PONs, Simulation (OMNeT++, GNS3). \\
		\textbf{Miscellaneous}			& Troubleshooting, Horizon 2020 Project Management, Office Suite, \LaTeX. \\
		\textbf{Languages} 				& Greek (native), English (C2), German (C1).
	\end{tabular}

	\section{Voluntary Activities and Memberships}
	\vspace*{0.125cm}	
	\begin{EntryDatedLogo}{University of Western Macedonia}{https://uowm.gr}{Mar. 2016 - 2018}{Author of educational material}{-1.1cm}{uowm}{0.6}
		\begin{Itemize}
			\item Author of original education material for the course "Network Design": \url{https://github.com/cdalamagkas/network-design-labs}
			\item Curriculum includes Cisco and Mikrotik routing and switching.
		\end{Itemize}
	\end{EntryDatedLogo}

	\vspace*{0.5cm}

	\begin{EntryDatedLogo}{Institute of Electrical and Electronics Engineers}{https://www.ieee.org/}{Sep. 2013 -- Now}{IEEE Member}{-0.5cm}{ieee}{0.6}
	\end{EntryDatedLogo}

	%\nocite{*}
	%\vspace*{0.125cm}
	%\printbibliography[title={Publications}]


\end{document}
